---
title: "Project Algo2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

&nbsp;

# Overview
 
**Algo2** encompasses a set of systematic trading strategies that, when employed collectively, aspire to consistently outperform the S&P 500 index by delivering superior returns while reducing risks.

&nbsp;

# Approach

Our approach commences with a collection of diverse individual strategies encompassing various trading styles and directions. The table below provides a high-level overview of these strategies employed within the portfolio, with specific details deliberately withheld. It also includes links to daily trading performance for further insights. These individual strategies are subsequently combined to form a portfolio to enhance risk-adjusted return.

&nbsp;

```{r table2, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- "
| No. | Description | Style | Direction | Performance  |
|:--:|:------------------|:----:|:----:|:----:|
| 1 | The strategy uses leverage to amplify benchmark returns during bull markets and switches to Treasury bills to control risks during bear markets. | Leverage trading | Long | [Link]() |
| 2 | The monthly rebalanced strategy intelligently allocates capital to the most promising stock and bond index funds, respectively, using a sliding-window historical performance analysis as its guiding principle. | Sector rotation | Long | [Link]() |
| 3 | The strategy actively searches for stocks exhibiting the most robust momentum, characterized by a consistent upward trajectory, and anticipates sustained growth in the foreseeable future. | Trend-following | Long | [Link]() |
| 4 | The strategy involves buying high-momentum stocks with the strongest momentum during bull market, and employs various exit algorithms to secure profits. | Trend-following | Long | [Link]() |
| 5 | The strategy aims to identify stocks that are in an uptrend but exhibit low volatility, with the belief that these stocks present an opportunity for a more consistent and steady price appreciation. | Trend-following | Long | [Link]()
| 6 | The strategy is designed to seize the majority of pullbacks within an uptrend when the stocks become oversold, based on pullback sizes. | Mean-reversion | Long | [Link]() |
| 7 | The strategy, while also aiming at profit from pullbacks within an uptrend, employs a more complex process based on technical indicators to select stocks. | Mean-reversion | Long | [Link]() |
| 8 | The strategy involves short-selling stocks using RSI as a hedge when the overall market is in a downtrend. | Mean-reversion | Short | [Link]() |
| 9 | The strategy aims to identify stocks that have experienced a significant recent surge in price, anticipating a high probability of correction and a return to their mean or average value. | Mean-reversion | Short | [Link]() |
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```

&nbsp;